Portfolios of fishing permits and species reduce risk but adjusting fishing strategy is risky

### 2016-09-09 portfolio/text/anderson-etal-rev-pfx.tex
Early draft of abstract, other text
Title brainstorm

\title{Portfolios of fishing permits and species
reduce risk but adjusting fishing strategy is risky}
\author{
Sean C. Anderson$^1$,
Eric J. Ward$^2$,
Milo D. Adkison$^3$,
Anne H. Beaudreau$^3$,\\
Richard E. Brenner$^4$,
Alan C. Haynie$^5$,
Andrew O. Shelton$^2$,\\
Jennifer C. Shriver,
Jordan T. Watson
}

@@

\vspace{-1cm}

@@

>>>>

\title{Portfolios of fishing permits and species
reduce risk but adjusting fishing strategy is risky\\
Portfolio benefits to fishers
depend on approach to diversification\\
Portfolio benefits of income diversification
are unavailable to many fishermen\\
Effect of species diversity on income variability
depends on fishing strategy\\
Effect of species diversity on revenue risk
depends on diversification approach\\
}
\author{
Sean C. Anderson$^1$,
Eric J. Ward$^2$,
Milo D. Adkison$^3$,
Anne H. Beaudreau$^3$,\\
Richard E. Brenner$^4$,
Alan C. Haynie$^5$,
Andrew O. Shelton$^2$,\\
Jennifer C. Shriver,
Jordan T. Watson,
\ldots
}

@@

% \vspace{-1cm}

@@

\clearpage
